```{r data generation, echo = FALSE, results = "hide"}
mu <- sample(seq(50, 80, 5), 1)
sigma <- sample(c(5, 8, 10), 1)
x0 <- round(mu + sample(c(-1.5,-1,-0.5,0.5,1,1.5),1)*sigma,1)

sol <- round(pnorm(x0, mean = mu, sd = sigma), 4)
```

Question
========

The following figure shows a normal distribution with mean $\mu=`r mu`$ and standard deviation $\sigma=`r sigma`$. The shaded region represents $P(X \le `r x0`)$ for a normally distributed random variable $X$.    
```{r plot, echo=FALSE, fig.height=3.5, fig.width=3.5, fig.cap=""}
x <- seq(mu - 4*sigma, mu + 4*sigma, length = 1000)
y <- dnorm(x, mu, sigma)

plot(x, y, type = "l", lwd = 2,
     xlab = "X", ylab = "Density")

xs <- x[x <= x0]
ys <- dnorm(xs, mu, sigma)

polygon(c(min(xs), xs, max(xs)),
        c(0, ys, 0),
        col = "lightblue",
        border = NA)

abline(v = x0, lty = 2)
```

Compute the probability represented by the shaded area. Round your answer to four decimal places.

Solution
========

The required probability is

$$
P(X \le `r x0`)
=
\Phi\left(
\frac{`r x0`-`r mu`}{`r sigma`}
\right).
$$

The corresponding probability is

$$
P(X \le `r x0`) = `r sol`.
$$

Meta-information
================

extype: num
exsolution: `r sol`
extol: 0.0001